Mahotas: Open source software for scriptable computer vision

### 2012-12-29 paper.tex
BUG Clarify dates of release

Version 1.0 of mahotas has been released recently and this is now a mature,
well-tested package (the first version was made available over 4~years ago).
\footnote{Note for reviewers: the version currently available (0.9.6)
implements all functionality described in this manuscript. I will release it as
version 1.0 when this manuscript is accepted to coincide with publication.
Naturally, any bugs that are found and reported in the meanwhile will be
addressed.} Mahotas runs and is used on different versions of Unix (including
Linux, SunOS, and FreeBSD), Mac OS X, and Windows.

@@

\textbf{Code repository}\\
\textit{Name}: Github\\
\textit{Identifier}: https://github.com/luispedro/mahotas\\
\textit{Licence}: MIT\\
\textit{Date published}: Since 2010

>>>>

Version 1.0 of mahotas has been released recently and this is now a mature,
well-tested package (the first versions were made available over 4~years ago,
although the package was not named mahotas then). \footnote{Note for reviewers:
the version currently available (0.9.6) implements all functionality described
in this manuscript. I will release it as version 1.0 when this manuscript is
accepted to coincide with publication. Naturally, any bugs that are found and
reported in the meanwhile will be addressed.} Mahotas runs and is used on
different versions of Unix (including Linux, SunOS, and FreeBSD), Mac OS X, and
Windows.

@@

\textbf{Code repository}\\
\textit{Name}: Github\\
\textit{Identifier}: https://github.com/luispedro/mahotas\\
\textit{Licence}: MIT\\
\textit{Date published}: Since 2010. Some of the code had been previously made
available under other names.
